Reassessing the Impact of Dynamic Slicing in SFL

### 2018-11-19 paper/main.tex
results

% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PLDI'19]{ ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 24--26, 2019}{Phoenix, AZ, USA}
\acmYear{2019}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
%% This research aims to address the doubts surrounding the efficiency
%% of \sfl{}+\ds{} combination through the answer to the following
%% research questions (\RQ{}):

\newcommand{\rqone}{How often does DS miss faulty statements?}
%\newcommand{\rqtwo}{How much reduction in file size can DS obtain?}
\newcommand{\rqthree}{How effective is the \comb{} combination?}

%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}

\begin{itemize}[leftmargin=*]
\item[]{\footnotesize[(un)soundness]}~\textit{\rqone{}}
\item[]{\footnotesize[effectiveness]}~\textit{\rqthree{}}  
\end{itemize}

The first question addresses an important problem associated with
dynamic slicing techniques---that of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
important problem happens in our experiments. The second research
questions effectively evaluates the impact of the combination. To sum,
our results show that \Fix{write a paragraph about this...}

@@

\newpage

@@

%% To select a slicer implementation to run our experiments, we
%% considered two criteria: robustness as to support non-trivial programs
%% and efficiency as to support execution of our experiments in
%% reasonable time.  Unfortunately, we failed to find public
%% implementations satisfying these criteria.
%% For those reasons, we ded to implement a critical slicer for Java,
%% which is the language of the subjects in our dataset, \dfj{}.

@@

We describe the results of dynamic slicing alone in the following.

\Sof{@todo: after answering rqs add a subsection to discuss the performance of \ds{}}

\subsubsection{\textit{Does the critical slice include the faulty statements?}}

\subsubsection{\textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}}

\subsection{Results of \sfl{}+\ds{} Combination}

@@

@@

\pagebreak

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis
to explain that observation is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a large
number. As such, it inflates actual improvements and deceives paper
reviewers. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging researchers to adopt precise metrics,
such as \topatn{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first N components.

@@

%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
%% This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):

\begin{itemize}[leftmargin=*]
%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}  
\item[]{\footnotesize[soundness]}~\textit{How often DS misses faulty statements?}
\item[]{\footnotesize[effectiveness]}~\textit{How much reduction in file size can DS obtain?}  
\item[]{\footnotesize[effectiveness]}~\textit{How effective is the \comb{} combination?} 
\end{itemize}

To sum, our results show that \Fix{write a paragraph about this...}

@@

@@

%% To select a slicer implementation to run our experiments, we
%% considered two criteria: robustness as to support non-trivial programs
%% and efficiency as to support execution of our experiments in
%% reasonable time.  Unfortunately, we failed to find public
%% implementations satisfying these criteria.
%% For those reasons, we decided to implement a critical slicer for Java,
%% which is the language of the subjects in our dataset, \dfj{}.

@@

We describe the results of dynamic slicing alone in the following

\subsubsection{\textit{How often DS misses faulty statements?}}

From the t

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrrrrrrr}
		\toprule
		Project             & \#FS  & \# T & \# Ev & \#Bugs & \%  $\overline{in}$ &  \% top-k & \% in  \\ 
		\midrule
		\chart{} 	& 40 &  57  &  136 & 21 & 13.2\% & 0\% & 86.8\%   \\
		\closure{} 	& 56 &  10  &  81 & 6 & 0\% & 3.7\% & 96.3\%   \\
		\lang{} 	& 204 &  90  &  447 & 59 & 0\% & 0\% & 100\%   \\
		\cmath{} 	& 299 &  112  &  438 & 86 & 8\% & 2.1\% & 89.9\%   \\
		\mockito{} 	& 94 &  93  &  397 & 25 & 3.3\% & 3.5\% & 93.2\%   \\
		\jtime{} 	& 63 &  49  &  171 & 16 & 1.2\% & 0\% & 98.8\%   \\
				\midrule
				Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
		%		\lang{}             & 100\% &  90  &  59  \\
		%		\cmath{}           & 96.4\% & 111   & 86  \\   
		%		\closure{}         & 100 \%  & 10  & 6   \\   
		%		\chart{}            &  86.8\% &  57  &  21 \\ 
		%		\jtime{}           &  &     &    \\   
		%		\mockito{}     & 100\% & 25  & 38  \\    
	\end{tabular}
	\caption {\ds{} performance evaluation}
\end{table*}
\normalsize

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{2pt}
	\begin{tabular}{lrrrrrrrr}
		\toprule

		Project             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
		\midrule

			\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
			\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
	\end{tabular}
	\caption {\sfl{}+\ds{} performance evaluation}
\end{table*}
\normalsize

@@
